---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# crs

<!-- badges: start -->
<!-- badges: end -->

The goal of crs is to extract *map projection* metadata from in-memory spatial R
objects. The map projection is a set of parameters that describe a *coordinate
reference system* ('crs') and there are various systems that do so with
different sets of aliases and assumptions. With crs we are only obtaining the
value from various formats so that we can develop tools that use them rather
than concern ourselves with format-specific plumbing.

We cannot obtain a crs value from out of memory sources like files, database, or
URLs. Use another tool for that. 

## Installation

You can install the released version of crs from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("crs")
```

Install the development version of crs from [Github](https://github.com/hypertidy/crs). 

```r
## install.packages("remotes")
remotes::install_github("hypertidy/crs")
```

## Example

This is a basic example which shows you how to obtain the PROJ string from 
spatial objects (raster, or silicate):

```{r example, warning=FALSE}
library(crs)
library(raster)

## a spatial object
r <- raster::raster()
r[50:51] <- 10

crs_proj(r)

crs_proj(silicate::SC0(silicate::inlandwaters))
```

This also works for sp, and sf. The function `crs_epsg()` also works
for sf objects, and `crs_wkt()` for sf and sp objects for later system-level 
versions of the PROJ library. 

Now sp or sf objects: 

```{r sf}
sfx <- sf::read_sf(system.file("gpkg/nc.gpkg", package = "sf", mustWork = TRUE))
crs_proj(sfx)
crs_proj(as(sfx, "Spatial"))
crs_wkt(as(sfx, "Spatial"))
crs_epsg(sfx)
```

## Code of Conduct

Please note that the crs project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/1/0/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
